---
title: 'Supplementary material for "Focused median bias reduction"'

author:
  - name: "[Davide Benussi](https://davidebenussi.github.io/)"
    email: davide.benussi@phd.unipd.it
    affiliations: 
      - University of Padova
      - University of Warwick
    url: https://davidebenussi.github.io/
  - name: "[Ioannis Kosmidis](https://www.ikosmidis.com)"
    email: ioannis.kosmidis@warwick.ac.uk
    affiliation: University of Warwick
    url: https://www.ikosmidis.com
  - name: "[Alessandra Salvan](https://homes.stat.unipd.it/alessandrasalvan/en/home-2/)"
    email: salvan@stat.unipd.it
    affiliation: University of Padova
    url: https://homes.stat.unipd.it/alessandrasalvan/en/home-2/	
  - name: "[Nicola Sartori](https://homes.stat.unipd.it/nicolasartori/en/home-2/)"
    email: sartori@stat.unipd.it
    affiliation: University of Padova
    url: https://homes.stat.unipd.it/nicolasartori/en/home-2/
date: last-modified
date-format: long
format: md
---

# Directory structure

```{r}
#| echo: false
#| message: false
library("tinytable")
R_pkgs <- data.frame(Package = sort(c("brbetabinomial", "focuson",
                                      "BAMBI", "numDeriv", "future.apply",
                                      "brglm2", "MuMIn", "enrichwith",
                                      "detectseparation", "dplyr", "progressr", "tidyr",
                                      "mvtnorm", "tinytest", "ISLR2",
                                      "ordinal", "pracma", "likelihoodAsy",
                                      "ggplot2", "tinytable", "patchwork",
                                      "robustbase")))
for (pkg in R_pkgs$Package)
    library(pkg, character.only = TRUE)
s_info <- sessionInfo()
R_v <- s_info$R.version$version.string
R_pkgs_v <- R_pkgs |> transform(Version = sapply(R_pkgs$Package, function(pkg)
                                    s_info$otherPkgs[[pkg]]$Version))
rownames(R_pkgs_v) <- NULL
```

The directory `code/` contains the R scripts that reproduce all the
numerical experiments in the manuscript

> Benussi D, Kosmidis I, Salvan A, Sartori N (2026). Focused median bias reduction. https://arxiv.org/abs/2606.28597

and the Supplementary Material document [`fmedbr-supplementary.pdf`](fmedbr-supplementary.pdf).

Running those scripts populates the directory `results/` with the
results of those experiments.

Then, running the script `produce_outputs.R` generates all tables (in
the directory `tables/` in LaTeX format) and graphics (in the
directory `figures/` in PDF format) reported in the main text and the
Supplementary Material document.

# R version and contributed packages

All results are reproducible using `{r} R_v` and the contributed
packages
```{r}
#| echo: false
tt(R_pkgs_v)
```

The `focuson` R package is available [here](https://github.com/ikosmidis/focuson).

The `brbetabinomial` R package is available [here](https://github.com/eulogepagui/brbetabinomial).

# Reproducing the results

## Path

All scripts specify the path to the supplementary material path as
`base_dir`. This is currently set to `.` assuming that the working
directory in R is set to the current `git` repository. If this is not the
case for your setup, you should set `base_dir` appropriately.

## Details

The following table lists the R scripts that need to be executed in
order to reproduce the results. The table also lists the outputs from
each script, and their label if they are shown in the main text or the
Supplementary Material document. Some of the outputs are intermediate
results, so the scripts should be executed in the order shown.


| Script                                                    | Output                                                                       | Type   |
|-----------------------------------------------------------|------------------------------------------------------------------------------|--------|
| [beta-binomial.R](code/beta-binomial.R)                   | [beta-binomial.rda](results/beta-binomial.rda)                               |        |
| [biv-von-Mises-var1.R](code/biv-von-Mises-var1.R)         | [bvmsin-circular-variance.rda](results/bvmsin-circular-variance.rda)         |        |
| [fic.R](code/fic.R)                                       | [fic.rda](results/fic.rda)                                                   |        |
| [mahalanobis-distance.R](code/mahalanobis-distance.R)     | [mahalanobis-distance.rda](results/mahalanobis-distance.rda)                 |        |
| [mahalanobis-distance-2.R](code/mahalanobis-distance-2.R) | [mahalanobis-distance-2sample.rda](results/mahalanobis-distance-2sample.rda) |        |
| [marginal-effects.R](code/marginal-effects.R)             | [marginal-effects.rda](results/marginal-effects.rda)                         |        |
| [ordinal-superiority.R](code/ordinal-superiority.R)       | [osm.rda](results/osm.rda)                                                   |        |
| [weibull.R](code/weibull.R)                               | [weibull.rda](results/weibull.rda)                                           |        |
| [produce_outputs.R](produce_outputs.R)                    | [beta-binomial.tex](tables/beta-binomial.tex)                                | Table  |
|                                                           | [bvmsin-circular-variance.tex](tables/bvmsin-circular-variance.tex)          | Table  |
|                                                           | [fic.tex](tables/fic.tex)                                                    | Table  |
|                                                           | [mahalanobis-distance.tex](tables/mahalanobis-distance.tex)                  | Table  |
|                                                           | [mahalanobis-distance-2sample.tex](tables/mahalanobis-distance-2sample.tex)  | Table  |
|                                                           | [osm.tex](tables/osm.tex)                                                    | Table  |
|                                                           | [weibull1.tex](tables/weibull1.tex)                                          | Table  |
|                                                           | [weibull5.tex](tables/weibull5.tex)                                          | Table  |
|                                                           | [weibull10.tex](tables/weibull10.tex)                                        | Table  |
|                                                           | [marginal-effects.pdf](figures/marginal-effects.pdf)                        | Figure |
|                                                           | [marginal-effects-cover.pdf](figures/marginal-effects-cover.pdf)             | Figure |









